Intersection of non-matching grids of different dimensions

### 2016-09-28 paper_intersections.tex
Minor fixes, fix line numbering in algorithm2,3 of intersection 23d.

  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{$I$ with IPs on $S_3$ boundary, partially filled $F$}
  \KwOut{all IPs in $I$, complete $F$}

  \nllabel{line:12edges}
  \lFor{edge $e$ of $S_4$}{$L[e]$ = intersection($e, S_3$)} 
  \For{unmarked edge $e$ of $S_4$}{
    $p=L[e]$\;
    \uIf{ $p$ is inside of $e$}{ 
        \nllabel{line:edge_faces}        
        $(f_0,\ f_1)$ = edge faces($e$)
    } 
    \Else($p$ on the vertex $v$ of $S_4$){       
            $(f_0,\ f_1)$ = vertex faces($v$)   \tcp*{Algorithm \ref{algo:vertex_faces}}
    }    
    \uIf{ $p$ is on boundary of $S_3$ }{
         $p$ lies on edge or vertex $x \in M_4$\;
         $q=F_g[x]$\tcp*{$q$ is already computed $p$}
         \lIf{$F_p[q]=x$}{$F_p[q]=f_1$}
         \lElse{$F_g[f_0]=q$}
         $F_g[x]=-1$\tcp*{remove the backlink}
    }
    \Else{
         append $p$ to $I$\;
         $F_g[f_0]=p$\tcp*{overwrites the backlink}
         $F_p[p]=f_1$\;
         mark all edges coincident with $p$
    }   
  }

@@

  \SetKw{return}{return}
  \SetKw{edgefaces}{edge faces}
  \DontPrintSemicolon
  \KwIn{vertex $v$ of $S_4$, $L[:]$ intersection results for edges of $S_4$}
  \KwOut{$(x_1, x_2)$, $x_1, x_2 \in M_4$, coincident with $v$ and intersected by the plane of $S_3$}
  $e_0,\ e_1,\ e_2$ edges coincident with $v$ oriented out of $v$
  $s[i] = L[e_i]$, for $i=0,1,2$, \;
  \nllabel{line:two_degenerated}
  \uIf{$s[:]$ have 1 non-degenerate edge $e$}{
    \return pair of degenerate edges sorted according to \edgefaces($e$)    
  }
  \nllabel{line:one_degenerated}
  \uElseIf{ $s$ have 1 degenerate edge $e$}{
    $f$ is face oposite to $e$
    \uIf{other two edges $e_a$, $e_b$ have different sign}{
        $z=\edgefaces(e_a)$\;
        replace $g\in z$, $g\ne f$ with $e$
        \return $z$
    }\lElse{
        append IP of $v$ to $J$
        \return anything\;
    }
  }
  \nllabel{line:different_sign}
  \uElseIf{ $s$ have edge $e$ with sign oposite to other two}{
    \return edge faces($e$)\;
  }
  \nllabel{line:same_signs}
  \Else($s$ have all signs same){
    append IP of $v$ to $J$
    \return anything\;
  }  
\end{algorithm}

Algorithm \ref{algo:collect_23_ip_edges} use the line-triangle intersection algorithm for the edges of $S_4$ (line \ref{line:12edges}).
The loop produce IPs from interior of $S_3$ and possibly those already computed IPs with special position on vertex or edge of $S_4$. 
Every edge $e$ of $S_4$ is oriented so that the pair of adjacent faces $f_0$, $f_1$ apear in the same order on the intersection polygon when the 
IP of $e$ have negative sign (see Figure \ref{fig:plucker_products}). The function "edge faces" used on line \ref{line:edge_faces} and later on 
use the sign of the intersection to return the pair of faces in the correct order. 
Similarly the function "vertex faces" (Algorithm \ref{algo:vertex_faces}) described latter on
returns pair of generalized faces (face or edge) possibly adjacent to the IP $L[e]$ at the vertex $v$ of $S_4$.

\subsubsection{Vertex Faces Algorithm}
This function get an IP $p$ at vertex $v$ of $S_4$ as a parameter. The IP is special vertex case of non-degenerate edge-triangle intersection. 
The functin returns pair of generalized faces of $S_4$ preceeding and succeeding $p$ on the polygons boundary in the case that $p$ is at interior of $S_3$.
Basic idea is to use the signs of IPs of the three edges coincident with $v$. 
Possible cases are:
\begin{itemize}
 \item {\bf All IPs have same sign.} (line \ref{line:same_signs}) We return any pair of faces.  $S_3$ is touching $S_4$ 
 in the vertex $v$, the polygon ddegenerates to the single IP $p$, no connectionn information from table $F$ necessary.
 \item {\bf Single IP have sign oposite to the other two.} (line \ref{line:different_sign}) Let $e$ be the edge of the single $IP$ with different sign. 
 The plane of $S_3$ separates $e$ from the other two edges so it goes through the faces adjacent to $e$. The order is detemined by the function edge faces.
 \item {\bf Single degenerated IP.} (line \ref{line:one_degenerated}) Let us denote $e$ the edge with degenerated IP and $f$ the face between the other two edges.
 The other two (non-degenerate) edges may have either oposite sign (the plane cut $S_4$) or the same sign (the plane touching $S_4$ at the edge $e$).
 In the first case, the call of edge faces for $e$ returns $(f_x,f)$ or $(f,f_x)$, then thr vertex faces function returns $(e, f)$ or $(f, e)$, respectively.

 The edge $e$ lies in the the singel edge
 \item {\bf Two degenerated IPs.} (line \ref{line:two_degenerated}) A face of $S_4$ lies in the plane of $S_3$, single edge $e$ have non-degenerate IP.
 We treat the two degenerate edges as special case of faces adjacent to $e$ and return them sorted like the faces given by edge faces fro edge $e$.
\end{itemize}

Either all signs are equal ($S_3$ touching $S_4$) wee , or
a single edge have the sign oposite to other twotwo edges have a sign oposite then the thi. of According to the

and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
with faces of $S_4$. Every point $p$ from the first part of the algorithm \notePE{I would use proper references instead, I got confused, what 'part of algorithm' is..} that is not a vertex of $S_3$ belongs to a face $f$ of $S_4$; we know from the order of the points
whether the face comes before or after the point in the intersection polygon; in the first case we set $F[0,f] =p$, in the second case we set $F[1,f]=p$. 
Every point $p$ from the second part of the algorithm lies on an edge $e$ which is between two faces $f_0$, $f_1$. The correct order of the faces on the 
intersection polygon is determined by the sign of the edge-triangle intersection. So, having the faces in the correct order we set $F[0,f_0]=p$ and $F[1, f_1]=p$.

Finally in the third part (Algorithm \ref{algo:order_23}), the table $F$ than allows us to modify array of successors $P$ and get $I$ in correct order as the list $K$.

>>>>

  \SetKw{And}{And}
  \SetKw{edgefaces}{edge faces}
  \SetKw{vertexfaces}{vertex faces}
  \DontPrintSemicolon
  \KwIn{$I$ with IPs on $S_3$ boundary, partially filled $F$}
  \KwOut{all IPs in $I$, complete $F$}

  \lFor{edge $e$ of $S_4$}{$L[e]$ = intersection($e, S_3$)}  \nllabel{line:12edges}
  \For{unmarked edge $e$ of $S_4$}{
    $p=L[e]$\;
    \uIf{ $p$ is inside $e$}{ 
        \nllabel{line:edge_faces}        
        $(f_0,\ f_1)$ = \edgefaces($e$)
    } 
    \Else($p$ at the vertex $v$ of $S_4$){       
            $(f_0,\ f_1)$ = \vertexfaces($v$,$L$)   \tcp*{Algorithm \ref{algo:vertex_faces}}
    }    
    \uIf{ $p$ is on boundary of $S_3$ }{
         $p$ lies on edge or at vertex $x \in M_4$\;
         $q=F_g[x]$\tcp*{$q$ is already computed $p$}
         \lIf{$F_p[q]=x$}{$F_p[q]=f_1$}
         \lElse{$F_g[f_0]=q$}
         $F_g[x]=-1$\tcp*{remove the backlink}
    }
    \Else{
         append $p$ to $I$\;
         $F_g[f_0]=p$\tcp*{overwrite the backlink}
         $F_p[p]=f_1$\;
         mark all edges coincident with $p$
    }   
  }

@@

  \SetKw{return}{return}
  \SetKw{edgefaces}{edge faces}
  \DontPrintSemicolon
  \KwIn{vertex $v$ of $S_4$, $L[:]$ intersection results for edges of $S_4$}
  \KwOut{$(x_1, x_2)$, $x_1, x_2 \in M_4$, coincident with $v$ and intersected by the plane of $S_3$}
  $e_0,\ e_1,\ e_2$ edges coincident with $v$ oriented out of $v$
  $s[i] = L[e_i]$, for $i=0,1,2$, \;

  \uIf{$s[:]$ have 1 non-degenerate edge $e$}{ \nllabel{line:two_degenerated}
    \return pair of degenerate edges sorted according to \edgefaces($e$)    
  }

  \uElseIf{ $s$ have 1 degenerate edge $e$}{\nllabel{line:one_degenerated}
    $f$ is face opposite to $e$
    \uIf{other two edges $e_a$, $e_b$ have different sign}{
        $z=\edgefaces(e_a)$\;
        replace $g\in z$, $g\ne f$ with $e$
        \return $z$
    }\lElse{
        append IP of $v$ to $J$
        \return anything\;
    }
  }

  \uElseIf{ $s$ have edge $e$ with sign oposite to other two}{ \nllabel{line:different_sign}
    \return edge faces($e$)\;
  }

  \Else($s$ have all signs same){ \nllabel{line:same_signs}
    append IP of $v$ to $J$
    \return anything\;
  }  
\end{algorithm}

Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_4$ (line \ref{line:12edges}).
The loop produces IPs in the interior of $S_3$ and possibly those IPs with special position on vertex or edge of $S_4$ already computed in Algorithm \ref{algo:colect_23_ip_triangle}. 
Every edge $e$ of $S_4$ is oriented so that the pair of adjacent faces $f_0$, $f_1$ appears in the same order on the intersection polygon when the 
IP on $e$ has a negative sign (see Figure \ref{fig:plucker_products}). The function \emph{edge faces}, used on line \ref{line:edge_faces} and later on,
uses the sign of the intersection to return the pair of faces ordered correctly. 
Similarly the function \emph{vertex faces} (Algorithm \ref{algo:vertex_faces}, described later)
returns a pair of generalized faces (face or edge) possibly adjacent to the IP $L[e]$ at the vertex $v$ of $S_4$.

\subsubsection{Vertex Faces Algorithm}
This function gets an IP $p$ at vertex $v$ of $S_4$ as a parameter. The IP is special vertex case of non-degenerate edge-triangle intersection. 
The function returns a pair of generalized faces of $S_4$ preceeding and succeeding $p$ on the polygons boundary in the case that $p$ is at interior of $S_3$.
The basic idea is to use the signs of IPs of the three edges coincident with $v$. 
Possible cases are:
\begin{itemize}
 \item {\bf All IPs have the same sign.} (line \ref{line:same_signs}) We return any pair of faces.  $S_3$ is touching $S_4$ 
 at the vertex $v$, the polygon degenerates into the single IP $p$, no connection information from table $F$ is necessary.
 \item {\bf Single IP has the opposite sign to the other two.} (line \ref{line:different_sign}) Let $e$ be the edge of the single IP with the different sign. 
 The plane of $S_3$ separates $e$ from the other two edges so it goes through the faces adjacent to $e$. The order is detemined by the function \emph{edge faces}.
 \item {\bf Single degenerated IP.} (line \ref{line:one_degenerated}) Let us denote $e$ the edge with degenerated IP and $f$ the face between the other two edges.
 The other two (non-degenerates) edges may have either the opposite sign (the plane is cutting $S_4$) or the same sign (the plane is touching $S_4$ at the edge $e$).
 In the first case, the call of edge faces for $e$ returns $(f_x,f)$ or $(f,f_x)$, then the vertex faces function returns $(e, f)$ or $(f, e)$, respectively.

 The edge $e$ lies in the the singel edge
 \item {\bf Two degenerated IPs.} (line \ref{line:two_degenerated}) A face of $S_4$ lies in the plane of $S_3$, single edge $e$ have non-degenerate IP.
 We treat the two degenerate edges as special case of faces adjacent to $e$ and return them sorted like the faces given by edge faces of edge $e$.
\end{itemize}

% Either all signs are equal ($S_3$ touching $S_4$) wee , or
% a single edge have the sign oposite to other twotwo edges have a sign oposite then the thi. of According to the 
% 
% 
% and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
% with faces of $S_4$. Every point $p$ from the first part of the algorithm \notePE{I would use proper references instead, I got confused, what 'part of algorithm' is..} that is not a vertex of $S_3$ belongs to a face $f$ of $S_4$; we know from the order of the points
% whether the face comes before or after the point in the intersection polygon; in the first case we set $F[0,f] =p$, in the second case we set $F[1,f]=p$. 
% Every point $p$ from the second part of the algorithm lies on an edge $e$ which is between two faces $f_0$, $f_1$. The correct order of the faces on the 
% intersection polygon is determined by the sign of the edge-triangle intersection. So, having the faces in the correct order we set $F[0,f_0]=p$ and $F[1, f_1]=p$.

Finally in the third part (Algorithm \ref{algo:order_23}), the table $F$ allows us to modify array of successors $P$ and get $I$ in the correct order as the list $K$.
